ICM testing

### 2022-08-11 Scripts/ASR_stocks.Rmd

---
title: "ICM testing"
output:
  word_document: default
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---

@@

```{r, echo=F, message=F, warning=F}
# OK, so using the ICES assessments here's what we get for North Sea cod.
library(readxl)
library(tidyverse)
library(rio)
library(ggthemes)

@@

@@

@@

  # All the results in a plot
  print(ggplot() +
          geom_line(data=did.it.work, aes(x=years,y=abund,color=sim)) +
          xlab("") +
          ylab("Abundance (1000s)") +
          geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') + scale_color_viridis_d(end = 0.75) +
          ggtitle(i) +
          geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?")))
  # Same thing but functional boxplots
  print(ggplot() +
          geom_line(data=quants, aes(x=years,y= med)) +
          geom_ribbon(data=quants, aes(x=years,ymax=U.50,ymin = L.50),alpha=0.5,fill='blue',color='blue') +
          geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          xlab("") + ylab("Abundance (1000s)") +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') +
          ggtitle(i)+
          geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?")))
  # Plotting how the estimate of r changes over time (which you can do when we have time varying inputs (e.g. Wgt, M, or maturity at age)
  print(ggplot(tst$r) +
          geom_line(aes(x=years,y=r,group=n.sims,color=n.sims)) +
          xlab("") +
          ylab("Estimated growth rate (r)") +
          #scale_y_continuous(breaks = seq(0,1.5,by=0.1)) +
          #scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') +
          scale_color_viridis_c(end = 0.75) +
          ggtitle(i))
}
```

>>>>

---
title: "ICM testing"
output:
  word_document: 
    reference_docx: template.docx
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---

@@

```{r, echo=F, message=F, warning=F, fig.width=6, fig.height=4}
# OK, so using the ICES assessments here's what we get for North Sea cod.
library(readxl)
library(tidyverse)
library(rio)
library(ggthemes)

@@

# summary plots for ALL stocks
for (i in unique(ASR_long$Stock)) {
  ASR_sub <- ASR_long %>%
    select(Year, Stock, type, age, value) %>%
    filter(Stock==i)
  maxage <- max(as.numeric(ASR_sub$age[!is.na(ASR_sub$value)]))
  maxYear <- max(ASR_sub$Year[!is.na(ASR_sub$value)])
  minYear <- min(ASR_sub$Year[!is.na(ASR_sub$value)])
  forplot <- ASR_sub[as.numeric(ASR_sub$age) < (maxage+1) & ASR_sub$Year %in% minYear:maxYear,]
  p1 <- ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
        geom_vline(data=forplot[is.na(forplot$value),], aes(xintercept=Year), colour="red") + facet_grid(type~as.numeric(age), scales="free_y") +
        theme_bw() + 
        ggtitle(i) +
    guides(x =  guide_axis(angle = 90)) 
  print(p1)

  if(!dir.exists(paste0("../Figures/", i))) dir.create(paste0("../Figures/", i))

  png(filename=paste0("../Figures/", i, "/data_summary_", i, ".png"), height=4, width=12, res=400, units="in")
  print(p1)
  dev.off()
}

@@

  # maxage <- max(as.numeric(ASR_sub$age[!is.na(ASR_sub$value)]))
  # maxYear <- max(ASR_sub$Year[!is.na(ASR_sub$value)])
  # minYear <- min(ASR_sub$Year[!is.na(ASR_sub$value)])
  # forplot <- ASR_sub[as.numeric(ASR_sub$age) < (maxage+1) & ASR_sub$Year %in% minYear:maxYear,]
  # 
  # # summary plots
  # print(ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
  #         geom_vline(data=forplot[is.na(forplot$value),], aes(xintercept=Year), colour="red") + facet_grid(type~as.numeric(age), scales="free_y") +
  #         theme_bw() + 
  #         ggtitle(i)
  # )

@@

  # All the results in a plot
  p2 <- ggplot() +
          geom_line(data=did.it.work, aes(x=years,y=abund,color=sim)) +
          xlab("") +
          ylab("Abundance (1000s)") +
          geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') + scale_color_viridis_d(end = 0.75) +
          ggtitle(i) +
          geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  # Same thing but functional boxplots
  p3 <- ggplot() +
          geom_line(data=quants, aes(x=years,y= med)) +
          geom_ribbon(data=quants, aes(x=years,ymax=U.50,ymin = L.50),alpha=0.5,fill='blue',color='blue') +
          geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          xlab("") + ylab("Abundance (1000s)") +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') +
          ggtitle(i)+
          geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  # Plotting how the estimate of r changes over time (which you can do when we have time varying inputs (e.g. Wgt, M, or maturity at age)
  p4 <- ggplot(tst$r) +
          geom_line(aes(x=years,y=r,group=n.sims,color=n.sims)) +
          xlab("") +
          ylab("Estimated growth rate (r)") +
          #scale_y_continuous(breaks = seq(0,1.5,by=0.1)) +
          #scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') +
          scale_color_viridis_c(end = 0.75) +
          ggtitle(i)

  print(p2)
  print(p3)
  print(p4)

  png(filename=paste0("../Figures/", i, "/runs_vs_vpa_", i, ".png"), height=4, width=6, res=400, units="in")
  print(p2)
  dev.off()
  png(filename=paste0("../Figures/", i, "/runs_vs_vpa_ribbon_", i, ".png"), height=4, width=6, res=400, units="in")
  print(p3)
  dev.off()
  png(filename=paste0("../Figures/", i, "/growth_", i, ".png"), height=4, width=6, res=400, units="in")
  print(p4)
  dev.off()
}
```
